Perimeter Control of Swarms

### 2019-01-03 paper.tex
Intro and Related started

\noindent\textit{Assumption 1:} The swarm used for the experiments consists of 200 agents randomly distributed~(Figure~\ref{fig:SampleSwarm200-1}).\\ 
\textit{Assumption 2:} The field effects and bias will be set as shown in~Figure~\ref{tab:DynamicPhysics1} with the weight adjuster $k_d = 0$ for the baseline.\\
\textit{Assumption 3:} All destination based experiments will have the weight adjuster set to $k_d = 100$.

>>>>

\noindentrilyn1\textit{Assumption 1:} The swarm used for the experiments consists of 200 agents randomly distributed~(Figure~\ref{fig:SampleSwarm200-1}).\\ 
\textit{Assumption 2:} The field effects and bias will be set as shown in~Figure~\ref{tab:DynamicPhysics1} with the weight adjuster $k_d = 0$ for the baseline.\\
\textit{Assumption 3:} All destination based experiments will have the weight adjuster set to $k_d = 100$.
